POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2024-01-10 existing-mechanisations/existing-mechanisations.tex
Add table and BibTeX for existing mechanisations.

\subsection{Template}
Abstract

\subsubsection{Approach}
\begin{itemize}
\item Proof assistant
\item 
\end{itemize}

\subsubsection{Quotes about challenges encountered}

\subsubsection{Suggestions in the paper}

>>>>

\subsection{Approaches}
\begin{tabular}{l|c|c|c|c|l}
  Reference          & Proof assistant & Linearity & Binders & Coinduction & Limitations \\\hline
  \cite{Tirore:2023} &&&&& \\
  \cite{Cruz-Filipe2021} &&&&& \\
  \cite{Pohjola2022} &&&&& \\
  \cite{Tassarotti2017} &&&&& \\
  \cite{Thiemann2019} &&&&& \\
  \cite{Goto2016} &&&&& \\
  \cite{Affeldt2008} &&&&& \\
  \cite{Scagnetto2002} &&&&& \\
  \cite{Hirschkoff1997} &&&&& \\
  \cite{Melham1994} &&&&& \\
  \cite{Ait-Mohamed1994} &&&&& \\
  \cite{Rockl2003} &&&&& \\
  \cite{Rockl2001} &&&&& \\
  \cite{Henry-Greard1999} &&&&& \\
  \cite{Miller2023} &&&&& \\
  \cite{Gordon1996} &&&&& \\
  \cite{Gay2001} &&&&& \\
  \cite{Despeyroux2000} &&&&& \\
  \cite{Gillard2000} &&&&& \\
  \cite{Honsell2001} &&&&& \\
  \cite{Perera2018} &&&&& \\
  \cite{Watkins2008} &&&&& \\
  \cite{Tiu2010} &&&&& \\
  \cite{Cervesato2007} &&&&& \\
  \cite{Baelde2014} &&&&& \\
  \cite{Bengtson2009} &&&&& \\
  \cite{Orchard2016} &&&&& \\
  \cite{Castro2020} &&&&& \\
  \cite{Zalakain2019} &&&&& \\
  \cite{Petz2016} &&&&& \\
  \cite{Bock2016} &&&&& \\
  \cite{Xi2016} &&&&& \\
  \cite{Hirsch2022} &&&&& \\
  \cite{Cruz-Filipe2021b} &&&&& \\
  \cite{Maksimovic2015} &&&&& \\
  \cite{Parrow2014} &&&&& \\
  \cite{Bengtson2016} &&&&& \\
  \cite{Kahsai2008} &&&&& \\
  \cite{Bengtson2007} &&&&& \\
  \cite{Castro-Perez2021} &&&&& \\
  \cite{Gay2020} &&&&& \\
  \cite{Brady2017} &&&&& \\
  \cite{Hinrichsen2019} &&&&& \\
  \cite{Sergey2017} &&&&&
\end{tabular}

\subsection{Existing experiences and suggestions}
In this section, we collect quotes about experiences attempting to mechanise process calculi and related systems, as well as suggestions proposed by other authors.

\subsubsection{Quotes about challenges encountered}
This section collects quotes about challenges encountered using various techniques for mechanisation.

\subsubsection{Quotes about effort on technical lemmas vs.\ effort on actual content}
This section collects quotes about the amount of effort spent on technical lemmas required by the mechanisation technique versus the amount of effort spent on the theorems of interest.

\subsubsection{Quotes about suggestions for improvements in proof assistant technology}
This section collects quotes suggesting improvements in proof assistant technology and/or mechanisation techniques.
